Malacology: A Programmable Storage System

### 2016-10-09 paper/paper.tex
paper: add some chub
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{table*}
\centering
\begin{tabular}{  l | l | l | l | l}
\textbf{Interface}            &
\textbf{\text{*}}             &
\textbf{Provides...}          &
\textbf{Example in Storage} & \\ \hline
Load Balancing  & migration \& monitoring primitives   & \\
Versioning      & consistency primitives               & \\ 
Shared Resource & serialization \& batching primitives
                & \\
Durability      & persistence primitives
                & \\
Logical Device  & transaction \& atomicity primitives 
                & Swift/ZeroVM in situ storage \& compute [1] \\ 
\end{tabular}
\caption{The Malacology interfaces are commonly used abstractions used
internally in storage stacks.}
\label{table:implementation}
\end{table*}
% http://www.zerovm.org/zerocloud.html

>>>>

\begin{table*}
\centering
\begin{tabular}{  l | l | l | l | l}
\textbf{Interface}            &
\textbf{\text{*}}             &
\textbf{Provides...}          &
\textbf{Example in Storage} & \\ \hline
Versioning      & \cmark & consensus \& consistency primitives  & PAXOS in Chubby [2] \\ 
Shared Resource & \cmark & serialization \& batching primitives & \\
Logical Device  & \cmark & transaction \& atomicity primitives  & Swift/ZeroVM in situ storage \& compute [1] \\ 
Durability      &        & persistence primitives               & \\
Load Balancing  &        & migration \& monitoring primitives   & IndexFS~\cite{ren:sc2014-indexfs} \& GIGA+~\cite{patil:fast2011-giga} \\
\end{tabular}
\caption{The Malacology interfaces are commonly used abstractions used
internally in storage stacks.}
\label{table:implementation}
\end{table*}
% http://www.zerovm.org/zerocloud.html
% https://www.usenix.org/legacy/events/nsdi11/tech/full_papers/Bolosky.pdf
% https://www.cs.utexas.edu/users/lorenzo/corsi/cs380d/papers/paper2-1.pdf
